\documentclass{article}
\usepackage{JBpack}
\usepackage{fancyhdr, fancybox}
\usepackage{extramarks, multicol} % Required for headers and footers
\usepackage{sectsty, hyperref}

\def\prog#1{
\vspace{.1in}\begin{mdframed} \begin{center} \textbf{Programming Reminders} \end{center}#1 \end{mdframed} }



\sectionfont{\underline}




\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=7.5in
\textheight=9.0in
\headsep=0.25in 
\headheight = 20pt
\hoffset = -.5in




\pagestyle{fancy}

\lhead{\large Due Date: \duedate}
%\chead{}
\rhead{\large Problem \problemnumber: \probname}
\renewcommand\headrulewidth{0.4pt} % Size of the header rule
\renewcommand{\labelitemii}{$\star$}







%%%%%% Assignment Data %%%%%%%%%%
\newcommand\problemnumber{F.4}
\newcommand\duedate{5/3/2019}
\newcommand\assignmenttype{Final Project}
\newcommand\foldername{\tt{FinalProject} }
\newcommand\filename{\tt{F4\_Prob220\_Name.py}\;\;}
\newcommand\probname{Problem 220: Heighway Dragon}
\newcommand\probnametwo{}







\begin{document}
\begin{multicols}{1}




%%%%%%% Title %%%%%%%%%%	
\begin{minipage}{\textwidth}
	 \begin{center} \shadowbox{\begin{Bcenter} \Huge \underline{Problem \problemnumber} \vspace{.25in} \\  \Huge \textbf{\probname} \\ \Huge \textbf{\probnametwo}  \end{Bcenter}  }
	 
	 {\Large Due Date: \duedate
	 
	 Folder: \foldername
	 
	 File Name: \filename
	 
	 Points: 20 points}
	  \end{center}
 \end{minipage}

\columnbreak


%%%%% Learning Objectives %%%%%%%
%\begin{minipage}{.45\textwidth}
%	\begin{center}
%	
%	\textbf{\Large Learning Objectives}
%	
%	\doublebox{
%		\begin{Bitemize}
%			\item Consider properties of quadratic residues
%		\end{Bitemize}
%	} 
%	\end{center}
%\end{minipage}
\end{multicols}






%%%%%%% Background %%%%%%%%%%%%
\section*{Problem Background}
	Begin by looking at the Project Euler page for this problem, {\color{blue} \href{https://projecteuler.net/problem=220}{Problem 220}}.  We start with a two letter string, such as $D_0$ = ``Fa".  We define a sequence of strings $D_n$ iteratively by the rules:
	\begin{itemize}
		\item For every ``a" in the string, replace it with the string ``aRbFR"
		\item For every ``b" in the string, replace it with the string ``LFaLb"
	\end{itemize}
	Thus after every iteration, the string obviously get longer.  An example of this iterative process is given on the Project Euler page.
	
	The resulting string, after $N$ iterations, can be interpreted as a sequence of commands for a graphics program.  Imagine there is a bug sitting at the origin $(0,0)$ facing up the positive $y$-axis.  Each character of the string tells the bug to make one movement.  A character of ``F" tells the bug to move one unit forward, the character ``L" tells the bug to turn 90 degrees to the left, and the character ``R" tells the bug to turn 90 degrees to the right.  The bug follows the instructions of the string, and as it moves it leaves behind a trail which can be plotted on the screen.  
	
	Your goal will be to draw this trail, following the instructions of the string $D_N$.  You can then answer questions such as how the plot changes as you increase $N$.  Also, how does the plot change if you change the initial string.


	
	
 
 	
 	
 	
 	
 	
 	
 	

	
	
	
	
	
	
	
	
%	\prog{
%		\begin{itemize}
%			\item Create function: \tt{def func\_name(params):}
%			\item Loops syntax: \tt{for ii in range(N)}
%			\item Create empty list: \tt{my\_list = []}
%			\item Append to list: \tt{my\_list.append(new\_thing)}
%		\end{itemize}
%		}




%%%%%%%%%% Program Criteria %%%%%%%%%
\section*{Program Criteria}
	Write a program that does the following:
	\begin{itemize}
		\item Create a variable \tt{N} to represent the number of iterations to perform.
		\item Create a variable to contain the start string $D_0$.
		\item Generate  the string $D_N$ iteratively, and display the corresponding graph.
	\end{itemize}







%%%%%%%%% Deliverables %%%%%%%%%
\section*{Deliverables}
	
	
	Place the following in a folder named \foldername in your repository:
	\begin{itemize}
		\item A Python file \filename  that satisfies the program criteria.
		\item A PDF file \tt{F4\_Prob220\_Name.pdf} that describes how your program works.  This should be a description of how you went about solving this problem.  You should go into some detail about your solution method, but I don't want to see something about every \tt{if} statement and \tt{for} loop.  As an example of the type of description I'm looking for, see the file \tt{Goldbach\_explanation.doc} in the \tt{Final Problem} folder of my repo.
		\item In the same PDF, explain how you translated the string into graphics.  For instance, how did you keep track of the direction  the bug was pointing, and how did you ``turn" the bug in the code.
		\item List at least two full questions that you think could be asked about this problem.  Here is an example, which you may not use as one of your questions
		\begin{itemize}
			\item ``Do different values of $D_0$ make the graph grow more like a line, while others make it grow more like a circle (looping back on itself) as $n$ increases?  Or is it some combination of the two, a looping line?"
		\end{itemize}
		State your questions just as fully as the one above.  Then at least \textbf{try} to give some possible answer, using your code.  I'm not  looking for a proof.

	\end{itemize}

	
\end{document}
